---
title: "Client API reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Client API reference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This article documents every user-facing function in **socialinfrascorer**,
grouped by capability area. All functions communicate through Supabase Auth
and PostgREST. No private API URL is required.

## Environment requirements

| Variable | Required | Purpose |
|----------|----------|---------|
| `SUPABASE_URL` | Always | Supabase project URL |
| `SUPABASE_ANON_KEY` | Always | Supabase anon/publishable key |

**Credentials and safety:** The `SUPABASE_URL` is public. Use only the anon
(publishable) key client-side; never expose a service-role or secret key.

## Client setup

```{r, eval = FALSE}
library(socialinfrascorer)

cli = client(
  supabase_url    = Sys.getenv("SUPABASE_URL"),
  anon_key        = Sys.getenv("SUPABASE_ANON_KEY"),
  access_token    = NULL,
  refresh_token   = NULL
)
```

`client()` returns a lightweight list that stores connection parameters and
(after sign-in) session tokens.

## Authentication

```{r, eval = FALSE}
sign_up(client, email, password, name = NULL)
sign_in(client, email, password)
send_password_reset(client)
delete_account(client)
```

- `sign_up()` registers a new user; an authenticated client is returned
  in `$client` when the session is created immediately.
- `sign_in()` authenticates and returns `$client` (with tokens),
  `$session`, and the raw `$data`.
- `send_password_reset()` requires a signed-in session and triggers
  a reset email for the authenticated user.
- `delete_account()` calls a server-side RPC that deletes the
  authenticated user.

## Polygon lookup

```{r, eval = FALSE}
search_locations(client, query, country = NULL, state = NULL, limit = 5)
get_boundary_by_osm_id(client, osm_id)
get_boundary_by_location_id(client, location_id)
get_boundary_by_area_id(client, area_id)
get_boundary_by_place_name(client, query, country = NULL, state = NULL)
```

Lookup functions return boundary geometry. `search_locations()` returns
candidate rows for fuzzy matching; `get_boundary_by_place_name()` resolves
to a single boundary.

## Scorecard and sites

```{r, eval = FALSE}
get_scorecard(client, osm_id = NULL, location_id = NULL, limit = 100, offset = 0)
get_sites(client, location_id, limit = 1000)
```

- `get_scorecard()` returns density, diversity, dispersion, and composite
  scores. Filter by either `osm_id` or `location_id`.
- `get_sites()` returns a random sample of social-infrastructure sites
  within the given location (capped at `limit`).

## Request workflow

```{r, eval = FALSE}
submit_request(
  client, geometry,
  name         = NULL,
  display_name = NULL,
  place_name   = NULL,
  country      = "US",
  state        = NULL,
  theme_ids    = NULL
)

get_request_status(client, request_id)
get_requests(client, limit = 100, offset = 0)
```

### Parameters for `submit_request()`

- **`geometry`** — GeoJSON geometry list or JSON string (Polygon /
  MultiPolygon, CRS 4326).
- **`theme_ids`** — optional integer vector or CSV string (e.g. `c(1,3,4)`
  or `"1,3,4"`); `NULL` uses the server default.

Sites for the new area come from Overture Maps (open data). The retired
arguments `sites_grid_sqkm` and `n_keywords` are still accepted but ignored
with a warning.

## Account and usage

```{r, eval = FALSE}
get_subscription(client)
get_usage(client, start_date = NULL, end_date = NULL)
get_remaining_queries(client)
```

- `get_subscription()` returns the user's profile including tier.
- `get_usage()` summarises request and query counts in a date range.
- `get_remaining_queries()` returns the remaining monthly quota for the
  authenticated user.
