---
title: "Getting started with socialinfrascorer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with socialinfrascorer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Overview

**socialinfrascorer** lets you use the Social Infrastructure Scorecard from R.
If you use the [Social Infrastructure Scorecard Dashboard](https://github.com/timothyfraser/scorecard),
this package gives you programmatic access to the same data: view social
infrastructure sites (parks, community spaces, places of worship, and more),
request scorecards for new areas, and download results for analysis.

You need two environment variables: `SUPABASE_URL` and `SUPABASE_ANON_KEY`.
These are provided when you sign up for access.

## Installation

```{r install}
devtools::install_github(
  "timothyfraser/scorecard",
  subdir = "socialinfrascorer"
)
```

## Step 1 — Create a client

The `client()` function builds a lightweight configuration object that every
other function in the package requires.

```{r client}
library(socialinfrascorer)

cli = client(
  Sys.getenv("SUPABASE_URL"),
  Sys.getenv("SUPABASE_ANON_KEY")
)
```

## Step 2 — Authenticate

Most operations require an authenticated session. Use `sign_up()` once to
register, then `sign_in()` for subsequent sessions.

```{r auth}
# First time only
result = sign_up(cli, "you@example.com", "strong-password", name = "Your Name")

# Subsequent sessions
auth = sign_in(cli, "you@example.com", "strong-password")
authed = auth$client
```

The returned `authed` client carries your session tokens and is passed to all
downstream functions.

## Step 3 — Look up a neighborhood

You can find neighborhoods by OpenStreetMap ID, internal location ID, area ID,
or free-text place name.

```{r polygon}
# By OSM ID
poly = get_boundary_by_osm_id(authed, osm_id = 5128581)

# By place name search
candidates = search_locations(authed, query = "Ithaca", state = "NY")
boundary = get_boundary_by_place_name(authed, query = "Ithaca", state = "NY")
```

Example output (sample):

```text
# A tibble: 1 x 8
  location_id osm_id  place_name county   state country area_km2 geom_type
        84217 5128581 Ithaca     Tompkins NY    US       15.41   Polygon
```

## Step 4 — Browse themes and keywords

Social infrastructure is organised into themes (e.g. community spaces, parks,
places of worship). Browse what is available before submitting a request.

```{r themes}
themes = get_themes(authed)
keywords = get_theme_keywords(authed, theme_ids = c(1, 3, 4))
```

## Step 5 — Submit a scorecard request

Supply a GeoJSON polygon and, optionally, theme selections. The server
validates geometry, checks your quota, and starts asynchronous processing.

```{r submit}
geom = list(
  type = "Polygon",
  coordinates = list(list(
    c(-122.32, 47.60), c(-122.30, 47.60),
    c(-122.30, 47.62), c(-122.32, 47.62),
    c(-122.32, 47.60)
  ))
)

result = submit_request(
  client    = authed,
  area      = geom,
  theme_ids = c(1, 3, 4),
  query_grid_sqkm = 2
)
```

## Step 6 — Poll for completion and retrieve results

Processing takes a few minutes. Poll the request status and retrieve the
scorecard when ready.

```{r results}
Sys.sleep(30)
status = get_request_status(authed, result$request$id)

if (status$status[1] == "success") {
  scores = get_scorecard(authed, location_id = result$location_id)
  sites  = get_sites(authed, location_id = result$location_id)
}
```

## Step 7 — Check your account

```{r account}
get_subscription(authed)
get_usage(authed, start_date = "2025-01-01")
get_remaining_queries(authed)
get_requests(authed)
```

## Next steps

- Read the [Client API](client-api.html) article for a complete function
  reference with parameter details.
- See [Workflows](workflows.html) for an in-depth look at how requests are
  processed on the backend.
