---
title: "Workflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This article describes the end-to-end workflows supported by
**socialinfrascorer** and the server-side processing that happens behind
the scenes.

## User read-only workflow

These queries read data that already exists in the database.

```{r readonly}
library(socialinfrascorer)

cli = client(Sys.getenv("SUPABASE_URL"), Sys.getenv("SUPABASE_ANON_KEY"))
auth = sign_in(cli, Sys.getenv("EMAIL"), Sys.getenv("PASSWORD"))
authed = auth$client

# Search by place name
candidates = search_locations(authed, query = "Ithaca", state = "NY")

# Retrieve boundary
poly = get_boundary_by_osm_id(authed, osm_id = 5128581)

# Retrieve sites (up to 1 000; larger sets are randomly sampled)
sites = get_sites(authed, location_id = 42)

# Retrieve scorecard
scores = get_scorecard(authed, osm_id = 5128581)
```

## User request workflow

When a neighborhood is not yet scored, the user submits a request with a
valid polygon. The server then:

1. **Validates** the geometry (must be Polygon or MultiPolygon, CRS 4326,
   within the area-size limit).
2. **Uploads** the boundary and creates a `location` entry.
3. **Logs** the request in `public.requests` with status tracking fields:
   `grid`, `sites`, `scorecard` (all start `FALSE`), `status`, and
   `update_time`.
4. **Generates a population grid** — extracts the regional population
   raster, crops to the polygon extent, and converts to 1 sq km cells
   stored in `public.neighborhood_grid_cache`.
5. **Ingests sites** — once the grid is ready (`grid = TRUE`), the server
   queries Google Places API using the selected themes and
   `query_grid_sqkm` cell size. When complete, `sites` is set to `TRUE`.
6. **Calculates the scorecard** — density, diversity, and dispersion
   metrics are computed, the result row is inserted into
   `public.scorecard_result`, and `scorecard` is set to `TRUE`.
7. **Sets final status** to `"success"` with the current timestamp.

```{r request}
geom = list(
  type = "Polygon",
  coordinates = list(list(
    c(-122.32, 47.60), c(-122.30, 47.60),
    c(-122.30, 47.62), c(-122.32, 47.62),
    c(-122.32, 47.60)
  ))
)

result = submit_request(
  client    = authed,
  area      = geom,
  theme_ids = c(1, 3, 4),
  query_grid_sqkm = 2
)

# Poll until complete
Sys.sleep(30)
status = get_request_status(authed, result$request$id)
```

Processing typically takes a few minutes depending on polygon area and
theme selection.

## Account management

```{r account}
# Registration and login
sign_up(cli, "user@example.com", "password", name = "User Name")
auth = sign_in(cli, "user@example.com", "password")
authed = auth$client

# Password and account lifecycle
send_password_reset(authed)
delete_account(authed)

# Request history and quotas
get_requests(authed)
get_subscription(authed)
get_usage(authed, start_date = "2025-01-01")
get_remaining_queries(authed)
```

### Subscription tiers

Every user has a subscription tier. The **free** tier allows a limited
number of queries per month (currently 100 sq km queries). The
**developer** tier (for the core team) has no limit.

Usage is tracked as the product of `area` (polygon sq km) and `n_keywords`
for each request.

## Implemented client functions

### Authentication

| Function | Description |
|----------|-------------|
| `sign_up()` | Register a new user |
| `sign_in()` | Authenticate and receive session tokens |
| `send_password_reset()` | Trigger a password-reset email |
| `delete_account()` | Delete the authenticated account |

### Polygon lookup

| Function | Description |
|----------|-------------|
| `search_locations()` | Fuzzy search for candidate locations |
| `get_boundary_by_osm_id()` | Fetch boundary by OpenStreetMap ID |
| `get_boundary_by_location_id()` | Fetch boundary by internal ID |
| `get_boundary_by_area_id()` | Fetch boundary by area UUID |
| `get_boundary_by_place_name()` | Resolve a single boundary from name |

### Themes, sites, and scorecard

| Function | Description |
|----------|-------------|
| `get_themes()` | List social-infrastructure themes |
| `get_theme_keywords()` | List keywords for selected themes |
| `get_sites()` | Retrieve sites for a location |
| `get_scorecard()` | Retrieve scorecard metrics |

### Requests and account

| Function | Description |
|----------|-------------|
| `submit_request()` | Submit a scoring request |
| `get_request_status()` | Check one request's status |
| `get_requests()` | List request history |
| `get_subscription()` | Get subscription profile |
| `get_usage()` | Get usage summary |
| `get_remaining_queries()` | Get remaining monthly quota |
